---
title: "assignment_1"
author: "David Langenohl"
date: "29.10.2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Tidy up the working environment.
```{r}
rm(list = ls())
```

1. Assign the value of 2 to a variable called a and the value of 5 to `a` variable called `b`.
```{r}
a <- 2
b <- 5
```

2. Compute the sum, difference, product and ratio of a and b (a always in the first place) and store the results to four different variables called `r1`, `r2`, `r3`, and `r4`.
```{r}
r1 <- a+b
r2 <- a-b
r3 <- a*b
r4 <- a/b
```

3. Create a vector `v1` which contains the values stored within the four variables from step 2.
```{r}
v1 <- c(r1, r2, r3, r4)
```

4. Add a fifth entry to vector `v1` which represents `a` by the power of `b` (i.e. `a**b`).
```{r}
v1[5] <- a**b
```

5. Show the content of vector `v1` (e.g. use the `print` function or just type the variable name in a separate row).
```{r}
v1
```

6. Create a second vector `v2` which contains information on the type of mathematical operation used to derive the five results. Hence this vector should have five entries of values *sum, difference,…*.
```{r}
v2 <- c("sum", "difference","product", "ratio", "a by the power of b")
```

7. Show the content of vector `v2`.
```{r}
v2
```

8. Combine the two vectors `v1` and `v2` into a data frame called `df`. Each vector should become one column of the data frame so you will end up with a data frame having 5 rows and 2 columns.
```{r}
df <- data.frame(Results = v1, Operation = v2)
```

9. Make sure that the column with the data of `v1` is named *Results* and `v2` is named *Operation*.
```{r}
colnames(df)
```

10. Show the entire content of `df`.
```{r}
df
```

11. Show just the entry of the 3. row and 1. coloumn.
```{r}
df[3,1]
```
