---
title: "assignment_01"
author: "Etienne Stadler"
date: "31 10 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Aufgabe 1: Assign the value of 2 to a variable called a and the value of 5 to a variable called b.
```{r}
a <- 2
b <- 5
```
Aufgabe 2: Compute the sum, difference, product and ratio of a and b (a always in the first place) and store the results to four different variables called r1, r2, r3, and r4.
```{r}
r1 <- a+b
r2 <- a-b
r3 <- a*b
r4 <- a/b
```
Aufgabe 3: Create a vector v1 which contains the values stored within the four variables from step 2.
```{r}
v1 <- c(r1,r2,r3,r4)
```
Aufgabe 4: Add a fifth entry to vector v1 which represents a by the power of b (i.e. a**b).
```{r}
r5 <- a**b
v1[5] <- r5
```
Aufgabe 5: Show the content of vector v1 (e.g. use the print function or just type the variable name in a separate row).
```{r}
print(v1)
```
Aufgabe 6: Create a second vector v2 which contains information on the type of mathematical operation used to derive the five results. Hence this vector should have five entries of values sum, difference,…
```{r}
v2 <- c("sum","diffrence","product","ratio","power")
```
Aufgabe 7: Show the content of vector v2.
```{r}
print(v2)
```
Aufgabe 8: Combine the two vectors v1 and v2 into a data frame called df. Each vector should become one column of the data frame so you will end up with a data frame having 5 rows and 2 columns.
```{r}
df <- data.frame(v2,v1)
print(df)
```
Aufgabe 9: Make sure that the column with the data of v1 is named Results and v2 is named Operation.
```{r}
colnames(df) <- c("Operation","Results")
```
Aufgabe 10: Show the entire content of df.
```{r}
print(df)
```
Aufgabe 11: Show just the entry of the 3 row and 1 column.
```{r}
df[3,1]
```
