---
title: "assignment_4"
author: "David Langenohl"
date: "12.11.2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = F}
## Load packages
libs = c("link2GI",
         "reshape2")
lapply(libs, require, character.only = TRUE)
```

```{r, include = F}
# Set pathes -------------------------------------------------------------------
if(Sys.info()[4] == "PC"){
  username <- "David"
} else if(Sys.info()[4] == "DESKTOP-LKKGU08"){
  username <- "hhans"
} else{print("You need to configure the filepath_base yourself!")}
## the if-else-loop sets the filepath depending on the system used ("PC" = PC, "DESKTOP-LKKGU08" = Laptop)

filepath_base <- paste0("C:/Users/", username, "/Google Drive/Studium/WiSe19/mpg-envinsys-plygrnd/data_analysis/")

# Set project specific subfolders -------------------------------------------------------------------
project_folders <- c("output/", "src/", "data/")

envrmt <- initProj(projRootDir = filepath_base,
                   projFolders = project_folders, 
                   path_prefix = "path_", 
                   global = FALSE)
```

First step: rename the file (without blank spaces and *-*) and save it in csv-format.
Second step: read in the data.
```{r}
crop_yield <- read.csv(paste0(envrmt$path_data, "crop_yield_not_clean.csv"), skip = 6, sep = ";", dec = ",")
crop_yield <- crop_yield[-c(8926:nrow(crop_yield)),] # remove last few rows, that contain not needed data
```

Name first three coloumns and keep the other names as they are.
```{r}
names(crop_yield) <- c("Jahr", "ID", "Ort", names(crop_yield[,4:ncol(crop_yield)]))
```

Replace missing values by NA and change decimal seperator from "," to ".".
```{r, warning = F}
for(c in colnames(crop_yield)[4:ncol(crop_yield)]){
  crop_yield[, c][crop_yield[, c] == "."] <- NA # replace missing values (cells with only ".") by NA  
  crop_yield[, c] <- as.numeric(sub(",", ".", as.character(crop_yield[, c]))) #replace "," as decimal seperator, by "." and convert numbers from factors to numerics (convert them to characters before that, as, otherwise, there might occur problems while converting)
}
```

Create a long format; not needed here, just testing it.
```{r}
crop_yield_long <- melt(crop_yield, id.vars = c("Jahr", "ID", "Ort")) 
```

Split the information of the "Ort" coloumn into seperate coloumns "Stadt", "Kreis", "Sonstiges"
```{r}
ort <- strsplit(as.character(crop_yield$Ort), ",")

ort_df <- lapply(ort, function(i){
  p1 <- sub("^\\s+", "", i[1])  # trim leading white spaces
  if(length(i) > 2){
    p2 <- sub("^\\s+", "", i[2])
    p3 <- sub("^\\s+", "", i[3])
  } else if (length(i) > 1){
    p2 <- sub("^\\s+", "", i[2])
    p3 <- NA
  } else {
    p2 <- NA
    p3 <- NA
  }
  data.frame(A = p1,
             B = p2,
             C = p3)
})
# if an entry of the "ort" list contains one entry, it is stored in the first coloumn of ort_df, if it contains two entries, they are stored on the first and second coloumn, three entries are stored in all three coloumns;also, the loop trims leading white spaces in the entries of the "ort" list
ort_df <- do.call("rbind", ort_df) #converts ort_df from list to data frame
```

Sort the information according the several places and handle missing entries.
```{r}
## if there is **no** NA in an row within the coloumn C, then, in this row, the entry of coloumn A stays in coloumn A (= 1), the entry of coloumn C(= 3) is placed in column B and the entry of coloumn B (= 2) is moved to coloumn C
# this way, "Kreisfreie Stadt" always stands in the coloumn B (was sometimes in column B and sometimes in coloumn C before), additional information like "Landeshauptstadt" is situated in the coloumn C
ort_df[!is.na(ort_df$C),] <- ort_df[!is.na(ort_df$C), c(1,3,2)]

sum(is.na(ort_df$B)) # 2006 rows still do not have an entry in coloumn B; so next: filling those 

## if an entry in the first coloumn contains "-kreis" it is a "Landkreis" -> write that into coloumn B IF column B has no entry yet
for(r in seq(nrow(ort_df))){
  if(is.na(ort_df$B[r]) & grepl("kreis", tolower(ort_df$A[r]))){
    ort_df$B[r] <- "Landkreis"
  }
}

sum(is.na(ort_df$B)) # 714 rows still without entry -> what is left, are federal states and some cities

## federal states have a special ID consisting of just two numbers, ranging from 01 to 15. So next, the IDs are merged with ort_df and "Bundesland" is written in coloumn B for those rows with two numbers in their ID. columns with an "DG" are titled "Land" as only "Deutschland" as "DG"
ort_df$ID <- crop_yield$ID # as the ort_df is sorted in the same order as crop_yield, it can be done that way

ort_df$B[is.na(ort_df$B) & nchar(as.character(ort_df$ID) == 2)] <- "Bundesland"
ort_df$B[ort_df$ID == "DG"] <- "Land"

sum(is.na(ort_df$B)) # no empty columns in B left
```

Merging ort_df with crop_yield.
```{r}
# as the ID is not unique in the whole data set, but unique for the year, the year coloumn is added to ort_df for merging purposes
ort_df$Jahr <- crop_yield$Jahr

crop_yield <- merge.data.frame(ort_df, crop_yield[,-3], by = c("Jahr", "ID"))

head(crop_yield)
```

