---
title: "assignement_2"
author: "David Langenohl"
date: "29.10.2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Tidy up the working environment.
```{r}
rm(list = ls())
```

Step 1.
Implement an if-then-else statement which prints “larger” if the number provided as variable *n* is larger than 1 and “equal or smaller” otherwise.
```{r}
n = 1

if(n > 1){
  print("larger")
} else {
  print("equal or smaller")
}
```

Step 2.
Extent a copy of the above statement (i.e. copy the entire if-then-else statement and include it a second time in your script in order to preserve both versions) which returns “equal” and “smaller” explicitly in addition to “larger”.
```{r}
n = 1

if(n > 1){
  print("larger")
} else {
  if(n == 1){
    print("equal")
  } else {
    print("smaller")
  }
} 
```

Step 3.
Implement a if-then-else statement which prints “even” if the number provided as variable *n* is even and which prints “odd” otherwise.
```{r}
n = 7

if(c(n %% 2) == 0){
  print("even")
} else {
  print("odd")
}
```
If *n %% 2* is *1*, the given number, divided by 2, has one position after decimal point. If it is *0*, it has no position after decimal point and, hence, it is even.

Step 4.
Copy the extended larger/equal/smaller if-then-else statement and include it into a for loop which shows that all three options are actually implemented in a correct manner by iterating over *n* from a number which is smaller 1, exactly 1 and larger than 1.
```{r}
for(n in c(0.5, 1, 1.5)){
  if(n > 1){
  print("larger")
    } else {
      if(n == 1){
      print("equal")
    } else {
      print("smaller")
    }
  } 
}
```

Step 5.
Extent a copy of the above loop and modify the loop and if-then-else statement in such a way, that the information on “larger” etc. is not printed on the screen but saved within a vector (i.e. a variable which will hold all three statements in the end). Print the content of this vector after the loop.
```{r}
result <- NULL

for(n in c(0.5, 1, 1.5)){
  if(n > 1){
  tmp <- "larger"
    } else {
      if(n == 1){
      tmp <- "equal"
    } else {
      tmp <- "smaller"
    }
  } 
  result <- c(result, tmp)
}
result
```

Step 6.
Extent a copy of the above modified loop in such a way, that the results are not saved in a vector but a list. Print the content of this list after the loop.
```{r}
result <- list()

for(n in c(0.5, 1, 1.5)){
  if(n > 1){
  tmp <- "larger"
    } else {
      if(n == 1){
      tmp <- "equal"
    } else {
      tmp <- "smaller"
    }
  } 
  result <- c(result, tmp)
}

result
```

Step 7.
Change the above modified loop in such a way, that the iteration is controlled by a *lapply* not by a for-loop. Save the returning information from the *lapply* function in a variable and print the content of this variable after the loop.
```{r}
n <- c(0.5, 1, 1.5)

result <- lapply(n, function(x){
  if(x > 1){
  return("larger")
    } else {
      if(x == 1){
      return("equal")
    } else {
      return("smaller")
    }
  } 
})

result
```

Step 8.
Finally change the above variable (i.e. do not modify the loop anymore but just include one more line) in such a way that the content is not printed as a nested list but a vector (i.e. flatten the list).
```{r}
result <- unlist(result)

result
```


