---
title: "Assignment 2"
author: "Jonas Viehweger"
date: "29 Oktober 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1

Implement an if-then-else statement which prints “larger” if the number provided as variable n is larger than 1 and “equal or smaller” otherwise.

```{r}
n <- 1
if(n > 1){
  print("larger")
} else {
  print("equal or smaller")
}
```

## 2

Extent a copy of the above statement (i.e. copy the entire if-then-else statement and include it a second time in your script in order to preserve both versions) which returns “equal” and “smaller” explicitly in addition to “larger”.

```{r}
if(n > 1){
  print("larger")
} else if(n == 1) {
  print("equal")
} else {
  print("smaller")
}
```

## 3

Implement a if-then-else statement which prints “even” if the number provided as variable n is even and which prints “odd” otherwise.

```{r}
n <- 1
if(n %% 2 == 1){
  print("odd")
} else {
  print("even")
}
```

## 4

Copy the extended larger/equal/smaller if-then-else statement and include it into a for loop which shows that all three options are actually implemented in a correct manner by iterating over n from a number which is smaller 1, exactly 1 and larger than 1.

```{r}
for(n in 0:2) {
  if(n > 1){
    print("larger")
  } else if(n == 1) {
    print("equal")
  } else {
    print("smaller")
  }
}
```

## 5

Extent a copy of the above loop and modify the loop and if-then-else statement in such a way, that the information on “larger” etc. is not printed on the screen but saved within a vector (i.e. a variable which will hold all three statements in the end). Print the content of this vector after the loop.

```{r}
result <- character()

for(n in 0:2) {
  if(n > 1){
    result <- c(result, "larger")
  } else if(n == 1) {
    result <- c(result, "equal")
  } else {
    result <- c(result, "smaller")
  }
}

print(result)
```

## 6

Extent a copy of the above modified loop in such a way, that the results are not saved in a vector but a list. Print the content of this list after the loop.

```{r}
result <- list()

for(n in seq(0.5,1.5,0.1)) {
  if(n > 1){
    result$larger <- c(result[["larger"]], n)
  } else if(n == 1) {
    result$equal <- c(result[["equal"]], n)
  } else {
    result$smaller <- c(result[["smaller"]], n)
  }
}

print(result)
```

## 7

Change the above modified loop in such a way, that the iteration is controlled by a lapply not by a for-loop. Save the returning information from the lapply function in a variable and print the content of this variable after the loop.

```{r}
result <- list()
n <- seq(0.5,1.5,0.1)

result <- lapply(n, function(n){
  if(n > 1){
    result <- "larger"
  } else if(n == 1) {
    result <- "equal"
  } else {
    result <- "smaller"
  }
})

print(result)
```

## 8

Finally change the above variable (i.e. do not modify the loop anymore but just include one more line) in such a way that the content is not printed as a nested list but a vector (i.e. flatten the list).

```{r}
result <- lapply(seq(0.5,1.5,0.1), function(n){
  if(n > 1){
    result <- list("larger" = n)
  } else if(n == 1) {
    result <- list("equal" = n)
  } else {
    result <- list("smaller" = n)
  }
})

flattenedResults <- unlist(result)

print(flattenedResults)
```