---
title: "chm_and_preprocessing_pretty_course_script"
author: "David Langenohl"
date: "19 11 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = F}
### Start ###
## Load packages
libs = c("link2GI",
         "raster",
         "lidR",
         "uavRst")

for(i in libs){
  if(lapply(i, require, character.only = TRUE) == F){
    install.packages(i)
  } else {}
}

## Set pathes 
if(Sys.info()[4] == "PC"){
  username <- "David"
} else if(Sys.info()[4] == "DESKTOP-LKKGU08"){
  username <- "hhans"
} else{print("You need to configure the filepath_base yourself!")}

filepath_base <- paste0("C:/Users/", username, "/Google Drive/Studium/WiSe19/GIS_Fernerkundung")

## Set project specific subfolders
project_folders <- c("output/", "src/",
                     "data/", "data/aerial/", "data/data_mof/", "data/grass/", "data/lidar/","data/tmp/",
                     "data/level0/", "data/level1/", "data/level2/", "data/level3/")

envrmt <- initProj(projRootDir = filepath_base,
                   projFolders = project_folders, 
                   path_prefix = "path_", 
                   global = FALSE)
```

Define status of switches.
preprocessing = True/False: defines if preprocessing shall be done; not necessary, if a preprocessed las-file is available (then set to False)
groundclassification = True/False: set to False, if groundclassification is not nessecary
```{r}
# define status of switches
preprocessing <- TRUE # if set to FALSE, the preprocessing step will be skipped 
groundclassification <- TRUE
```

Define projection.
```{r}
proj4 = "+proj=utm +zone=32 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0"
```

Get all .las files within the level0 (= unprocessed data) folder.
```{r}
las_files = list.files(envrmt$path_data_lidar,
                       pattern = glob2rx("*.las"),
                       full.names = TRUE)
```

Define Zhang et. al.  paramters (have a look at the lidR documentation).
```{r}
if(groundclassification)lground_params <- lidR::util_makeZhangParam(b = 5, dh0 = 6, dhmax = 7, s = 7, max_ws = 100)
```

Preprocessing.
```{r}
if (preprocessing){
  # preprocessing script to deal with LiDAR data  files as provided by the authority 
  # all files in a given directory will be checked for correct extent (0,0 coordinate propblem)
  # and georefrenced according to a given projection system 
  # optionally  they can be manually ground-classified (class2)
  # finally a lidR catalog of 200 by 200 meters is created and exported
  # the result is saved in a 
  #preprocessing check if extent and projection are correct, write lax file
  for(fn in las_files){
    las <-uavRst::correctLas(fn,proj4 = proj4)
    ##- maybe the ground (return class =2) has to be recalculated
    #   NOTE this needs a MASSIVE amount of CPU time
    if (groundclassification) lidR::lasground(las, "pmf",lground_params$ws, lground_params$th)
    sp::proj4string(las) <- sp::CRS(proj4,doCheckCRSArgs=TRUE)
    las = lidR::writeLAS(las,paste0(envrmt$path_data_level0,basename(fn)))
    rlas::writelax(paste0(envrmt$path_data_level0,basename(fn)))
  }
  ## setting up the lidR catalog
  mof <- lidR::catalog(envrmt$path_data_level0)
  sp::proj4string(mof) <- sp::CRS(proj4) # ETRS89 / UTM zone 32N
  lidR::opt_cores(mof) <- 4L
  lidR::opt_chunk_size(mof) = 500
  lidR::opt_chunk_buffer(mof) <- 10
  
  ## Clip catalog to the area of interest retile and reconfigure the catalog
  xl<-476174.
  yb<-5631386.
  xr<-478217. 
  yt<-5632894.
  
  aoimof<- lidR::lasclipRectangle(mof,
                                  xleft = yl,
                                  ybottom = yb,
                                  xright = xr,
                                  ytop = yt)
  
  lidR::writeLAS(aoimof,file.path(envrmt$path_data_level0,"las_mof.las"))
  writelax(file.path(envrmt$path_data_level0, "las_mof.las"))
  
  mof <- lidR::catalog(envrmt$path_dat_level1)
  sp::proj4string(mof) <- sp::CRS(proj4)
  lidR::opt_cores(mof) <- 4L
  lidR::opt_chunk_size(mof) = 200
  lidR::opt_chunk_buffer(mof) <- 0
  lidR::opt_output_files(mof) <- paste0(envrmt$path_data_level1,"{ID}")
  mof = catalog_retile(mof)
  sp::proj4string(mof) <- sp::CRS(proj4)
  saveRDS(mof,file= paste0(envrmt$path_data_level1,"las_mof.rds"))
  
} else {}
```

Plot the preprocessed file.
```{r}
mof <- readRDS(paste0(envrmt$path_data_level1,"las_mof.rds"))

### let see it
plot(mof)
```

Calculation of DSM and DTM.
```{r}
# Khosravipour et al. pitfree algorithm
dsm <- lidR::grid_canopy(mof, res = 0.5, lidR::pitfree(c(0,2,5,10,15), c(0, 2)))
raster::writeRaster(dsm,file.path(envrmt$path_data,"mof_dsm_all.tif"))
dtm = lidR::grid_terrain(mof, res=0.5,  algorithm = lidR::kriging(k = 10L))
raster::writeRaster(dtm,file.path(envrmt$path_data,"mof_dtm_all.tif"))
raster::plot(dtm)
raster::plot(dsm)
##- alternative way to create a CHM is to "normalize' the pointcloud by a given DTM
#chm<-lasnormalize(mof, dtm)
```

