---
title: "individual_tree_segmentation"
author: "David Langenohl"
date: "11.11.2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include = F}
#Load packages, needed for the tasks.
#The needed packages are written into *libs*, the *lapply* loops gives out, if they are installed (if not, do it individually) and, if so, reads #them in.

## Load packages
libs = c("link2GI",
         "raster",
         "lidR",
         "EBImage")
lapply(libs, require, character.only = TRUE)
```

```{r, include = F}
#Set the projects home directory and the folder pathes. The pathes can than be reached by (e.g) *envrmt$filepath_base*.

## Set pathes -------------------------------------------------------------------
if(Sys.info()[4] == "PC"){
  username <- "David"
} else if(Sys.info()[4] == "DESKTOP-LKKGU08"){
  username <- "hhans"
} else{print("You need to configure the filepath_base yourself!")}
### the if-else-loop sets the filepath depending on the system used ("PC" = PC, "DESKTOP-LKKGU08" = Laptop)

filepath_base <- paste0("C:/Users/", username, "/Google Drive/Studium/WiSe19/GIS_Fernerkundung")

## Set project specific subfolders -------------------------------------------------------------------
project_folders <- c("output/", "src/", "data/")

envrmt <- initProj(projRootDir = filepath_base,
                   projFolders = project_folders, 
                   path_prefix = "path_", 
                   global = FALSE)
```

Read and plot las-file
```{r}
# following this tutorial: https://github.com/Jean-Romain/lidR/wiki/Segment-individual-trees-and-compute-metrics

las <- readLAS(paste0(envrmt$path_data, "session_3/U4765630.laz"))
plot(las)
```

Classify ground points and height normalize the dataset.
```{r}
las = lasground(las, csf()) #works fine without the need to tune the parameters
#plot(las, color = "Classification")
las = lasnormalize(las, tin())
plot(las)
```

There are several methods to segment the tree in lidR the following will use a watershed, that is far to be the best, but is good enough for this easy to segment example.
First step: create a canopy height model (CHM).
```{r, fig.width = 10 ,fig.height = 10}
algo = pitfree(thresholds = c(0,10,20,30,40,50), subcircle = 0.2)
chm  = grid_canopy(las, 0.5, algo)
plot(chm, col = height.colors(50))
```

Optionally, the CHM can be smoothed by using the *raster* package (not faster!)
```{r, fig.width = 10, fig.height = 10}
# smoothing post-process (e.g. two pass, 3x3 median convolution)
ker = matrix(1,3,3)
chm1 = focal(chm, w = ker, fun = median)
chm1 = focal(chm1, w = ker, fun = median)

plot(chm1, col = height.colors(50)) # check the image
```

The segmentation can now be achieved with lastrees. Here I chose the watershed algorithm with a threshold of 4 meters. The point cloud has been updated and each point now has a number that refers to an individual tree (treeID). Points that not trees are assigned the id value NA.
```{r}
##EBImage package is needed for watershed, needs to be installed via the bioconductor project package
#install.packages("BiocManager")
#BiocManager::install("EBImage")
library(EBImage)

algo = lidR::watershed(chm, th_tree = 4)
las  = lastrees(las, algo)

# remove points that are not assigned to a tree
trees = lasfilter(las, !is.na(treeID))

plot(trees, color = "treeID", colorPalette = pastel.colors(100)) #worked out pretty good!
```

Compute hulls.
```{r}
hulls  = tree_hulls(las, func = .stdmetrics)
raster::spplot(hulls, "Z") # does not work; can not fix it right now
```

Optionally, the crowns can be plotted in a raster (if further processing shall be done with raster).In that case the function watershed can be used standalone:
```{r, fig.width = 10, fig.height = 10}
crowns = lidR::watershed(chm, th_tree = 4)()
plot(crowns, col = pastel.colors(100))
```

Once you are working with rasters the lidR package is not implied anymore. User can rely on the raster package for further analysis. For example:
```{r, fig.width = 10, fig.height = 10}
contour = rasterToPolygons(crowns, dissolve = TRUE) # takes years to process (and way to much RAM)

plot(chm, col = height.colors(50))
plot(contour, add = T)
```

