---
title: "assignment_7"
author: "David Langenohl"
date: "09.12.2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = F}
rm(list = ls())
source("../setEnvironment.R")
```

Variable-Selection-Function with following inputs:
- data = dataset, that shall be analysed  
- dep = dependend variables (y)  
- var = independent/describing variables, from that the best ones shall be found  
- AIC = set to TRUE, if best variables should be searched by *forward feature selection* (looking for the smalles AIC) [default = TRUE]  
- RMSE = set to TRUE, if best variables should be searched by *nfold cross validation* (looking for smallest AIC) [default = FALSE]  
- nfolds = number of folds to use in nfold-cross-validation [default = 3]  

```{r}
var_selection <- function(data, dep, vars,  AIC = T, RMSE = F, nfolds = 3){
  feature_selection <- function(data, dep, vars, nfolds = 3, AIC = T, RMSE = F,  selected_vars = NULL){
    if(c(AIC == T & RMSE == F) | c(AIC == F & RMSE == T)){
      
      results <- data.frame(Variable = NULL,
                            Adj_R_sqrd = NULL,
                            AIC = NULL,
                            RMSE = NULL,
                            RMSE_SD = NULL)
      
      for(v in seq(length(vars))){
        if(is.null(selected_vars)){
          formula <- paste(dep, " ~ ", paste(vars[v], collapse=" + "))
        } else {
          formula <- paste(dep, " ~ ", paste(c(selected_vars, vars[v]), collapse=" + "))
        }
        
        lmod <- lm(formula, data = data)
        
        se <- function(x) sd(x, na.rm = TRUE)/sqrt(length(na.exclude(x)))
        
        set.seed(v)
        data_random <- data[sample(nrow(data)),] #randomly shuffle data
        data_random$fold <- cut(seq(1,nrow(data_random)),breaks = nfolds,labels = FALSE) #create a fold coloumn
        tmp_df <- NULL
        for (i in seq(nfolds)){
          smpl <- which(data_random$fold == i)
          train <- data_random[smpl,]
          test <- data_random[-smpl,]
          lmod_cv <- lm(formula, data = train)
          pred <- predict(lmod_cv, newdata = test)
          obsv <- test[,dep]
          tmp <- data.frame(rmse = round(sqrt(mean((pred - obsv)^2, na.rm = TRUE)), 2),
                            rmse_sd = round(se((pred - obsv)^2), 2))
          tmp_df <- rbind(tmp_df, tmp)
        }
        
        results_tmp <- data.frame(Variable = vars[v],
                                  Adj_R_sqrd = round(summary(lmod)$adj.r.squared, 4),
                                  AIC = round(AIC(lmod), 4),
                                  RMSE = mean(tmp_df$rmse),
                                  RMSE_SD = mean(tmp_df$rmse_sd))
        
        results <- rbind(results, results_tmp)
      }
      
      if(!is.null(selected_vars)){
        formula <- paste(dep, " ~ ", paste(selected_vars, collapse=" + "))
        lmod <- lm(formula, data = data)
        sel_tmp_df <- NULL
        for (i in seq(nfolds)){
          smpl <- which(data_random$fold == i)
          train <- data_random[smpl,]
          test <- data_random[-smpl,]
          lmod_cv <- lm(formula, data = train)
          pred <- predict(lmod_cv, newdata = test)
          obsv <- test[,dep]
          tmp <- data.frame(rmse = round(sqrt(mean((pred - obsv)^2, na.rm = TRUE)), 2),
                            rmse_sd = round(se((pred - obsv)^2), 2))
          sel_tmp_df <- rbind(sel_tmp_df, tmp)
        }
        
        results_selected <- data.frame(Variable = paste0("all: ", paste(selected_vars, collapse=", ")),
                                       Adj_R_sqrd = round(summary(lmod)$adj.r.squared, 4),
                                       AIC = round(AIC(lmod), 4),
                                       RMSE = mean(sel_tmp_df$rmse),
                                       RMSE_SD = mean(sel_tmp_df$rmse_sd))
        results <- rbind(results_selected, results)
      }
      
      
      if(AIC == T & RMSE == F){
        best_var <- as.character(results$Variable[which(results$AIC == min(results$AIC))]) 
      }
      
      else if(AIC == F & RMSE == T){
        best_var <- as.character(results$Variable[which(results$RMSE == min(results$RMSE))]) 
      }
      
      return(c(best_var, results))
    }
    
    ## if both, FFS and CV, are set to True or False; print warnings
    else if(c(AIC == T & RMSE == T) | c(AIC == F & RMSE == F)){
      if(AIC == T & RMSE == T){
        warning("Two methods defined. Please choose only one of AIC = True or RMSE = True")
      }
      
      else if(AIC == F & RMSE == F){
        warning("No method defined. Please choose AIC = True or RMSE = True")
      }
    }
  }
  
  if(AIC == T & RMSE == F){
    selected_vars <- NULL
    best_var <- feature_selection(data = data, dep = dep, vars = vars, nfolds = nfolds)
    results_run <- data.frame(best_var[2:6])
    results_run$Variable <- as.character(results_run$Variable)
    results_run_old <- results_run
    act_var <- best_var[[1]] # which variable was best? 
    next_vars <- as.character(best_var[[2]][-which(best_var[[2]] == act_var)]) # take other variables for next run
    next_vars <- next_vars[-1]
    selected_vars <- c(selected_vars, act_var)
    
    i <- 1
    output <- data.frame(no_of_variables = i,
                         AIC = results_run$AIC[which(results_run$AIC == min(results_run$AIC))])
    
    
    while(any(results_run$AIC[2:nrow(results_run)] < results_run$AIC[1])){
      best_var <- feature_selection(data = data, dep = dep, vars = next_vars, selected_vars = selected_vars, nfolds = nfolds)
      results_run <- data.frame(best_var[2:6])
      results_run$Variable <- as.character(results_run$Variable)
      
      # implement if-statement, that breaks loop, if AIC becomes getting bigger than the last one
      if(results_run$AIC[which(results_run$AIC == min(results_run$AIC))] 
         < results_run_old$AIC[which(results_run_old$AIC == min(results_run_old$AIC))]) {
        results_run_old <- results_run
      }
      else if(results_run$AIC[which(results_run$AIC == min(results_run$AIC))] 
         > results_run_old$AIC[which(results_run_old$AIC == min(results_run_old$AIC))]) {break}
      
      act_var <- best_var[[1]]
      next_vars <- as.character(best_var[[2]][-which(best_var[[2]] == act_var)])
      next_vars <- next_vars[-1]
      if(length(next_vars) == 0){break} #quits loop, if all variables are used as selected variables
      selected_vars <- c(selected_vars, act_var)
      
      i <- c(i+1)
      output_tmp <- data.frame(no_of_variables = i,
                         AIC = results_run$AIC[which(results_run$AIC == min(results_run$AIC))])
      output <- rbind(output, output_tmp)
    }
    
    best_result <- data.frame(Variables = paste(selected_vars, collapse="; "),
                              AIC = results_run$AIC[which(results_run$AIC == min(results_run$AIC))])
    
    plot(AIC ~ no_of_variables, data = output, type = "b")
  }
  
  else if(AIC == F & RMSE == T){
    selected_vars <- NULL
    best_var <- feature_selection(data = data, dep = dep, vars = vars, nfolds = nfolds)
    results_run <- data.frame(best_var[2:6])
    results_run$Variable <- as.character(results_run$Variable)
    results_run_old <- results_run
    act_var <- best_var[[1]] # which variable was best? 
    next_vars <- as.character(best_var[[2]][-which(best_var[[2]] == act_var)]) # take other variables for next run
    next_vars <- next_vars[-1]
    selected_vars <- c(selected_vars, act_var)
    
    i <- 1
    output <- data.frame(no_of_variables = i,
                         RMSE = results_run$RMSE[which(results_run$RMSE == min(results_run$RMSE))])
    
    while(any(results_run$RMSE[2:nrow(results_run)] < results_run$RMSE[1])){
      best_var <- feature_selection(data = data, dep = dep, vars = next_vars, selected_vars = selected_vars, nfolds = nfolds)
      results_run <- data.frame(best_var[2:6])
      results_run$Variable <- as.character(results_run$Variable)
      
      # implement if-statement, that breaks loop, if RMSE becomes getting bigger than the last one
      if(results_run$RMSE[which(results_run$RMSE == min(results_run$RMSE))] 
         < results_run_old$RMSE[which(results_run_old$RMSE == min(results_run_old$RMSE))]) {
        results_run_old <- results_run
      }
      else if(results_run$RMSE[which(results_run$RMSE == min(results_run$RMSE))] 
         > results_run_old$RMSE[which(results_run_old$RMSE == min(results_run_old$RMSE))]) {break}
      
      act_var <- best_var[[1]]
      next_vars <- as.character(best_var[[2]][-which(best_var[[2]] == act_var)])
      next_vars <- next_vars[-1]
      if(length(next_vars) == 0){break} #quits loop, if all variables are used as selected variables
      selected_vars <- c(selected_vars, act_var)
      
      i <- c(i+1)
      output_tmp <- data.frame(no_of_variables = i,
                         RMSE = results_run$RMSE[which(results_run$RMSE == min(results_run$RMSE))])
      output <- rbind(output, output_tmp)
    }
        
    best_result <- data.frame(Variables = paste(selected_vars, collapse="; "),
                              RMSE = results_run$RMSE[which(results_run$RMSE == min(results_run$RMSE))])
    
    plot(RMSE ~ no_of_variables, data = output, type = "b")
  }
  print(best_result)
  return(best_result)

}
```
  
    
Example data.
```{r}
data <- read.table(paste0(envrmt$path_data, "feldfruechte_cleaned.csv"), sep = ";")
dep <- "Winterweizen"
vars <- c(names(data)[5:length(names(data))])
nfolds <- 3 # 3-fold cross validation
```
  
    
Use *forward feature selection*
```{r}
AIC_feature_selection <- var_selection(data = data, dep = dep, vars = vars, AIC = T)
```
  
    
Use *3-fold cross validation*
```{r}
RMSE_feature_selection <- var_selection(data = data, dep = dep, vars = vars, RMSE = T, AIC = F)
```



