---
title: "Assignment 07: Forward feature selection"
author: "Jonas Viehweger"
date: "05.12.2019"
output: html_document
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "R:/Studium/Marburg/WS19/mpg-envinsys-plygrnd/mpg-data-analysis-2019-jonasViehweger/")
```

### 1. Using mean RMSE from 3-fold cross validation as performance metric

```{r}
# Load already cleaned csv (no NA Values and wide format)
yields <- read.csv("../data/data_analysis/assignment_07/feldfruechte_cleaned_for_fs.csv", 
                      header = T, sep = ";", dec = ".")[,4:13]

# Set parameters
dfNames <- names(yields)
dep <- dfNames[1]
vars <- dfNames[-1]
selection_parameter <- "RMSE"

# Load forward feature selection script and run it
source("assignment_07/fwdFt.R")
result <- forward_feature_selection(yields, dep, vars, selection_parameter = selection_parameter)

plot(result$Performance, type = "b",
     main = "Performance of Model", xlab = "Number of Predictors", ylab = selection_parameter)
```

The selected predictors for the final model are __`r paste(result$Added.Variable, collapse=", ")`__. The final model has an __`r selection_parameter` of `r sprintf("%.2f", min(result$Performance))`__.

### Summary of final model
```{r}

formula <- paste(dep, " ~ ", paste(result$Added.Variable, collapse=" + "))
lmod <- lm(formula, data = yields)

summary(lmod)

```
---
### 2. Using AIC as performance metric

```{r}
selection_parameter <- "AIC"
result <- forward_feature_selection(yields, dep, vars, selection_parameter = selection_parameter)

plot(result$Performance, type = "b",
     main = "Performance of Model", xlab = "Number of Predictors", ylab = selection_parameter)
```

The selected predictors for the final model are __`r paste(result$Added.Variable, collapse=", ")`__. The final model has an __`r selection_parameter` of `r sprintf("%.2f", min(result$Performance))`__.

### Summary of final model
```{r}

formula <- paste(dep, " ~ ", paste(result$Added.Variable, collapse=" + "))
lmod <- lm(formula, data = yields)

summary(lmod)

```