---
title: "assignment_03"
author: "Etienne Stadler"
date: "5 11 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1: Read the data provided in the Excel file and “isolate” the tabulated information into a data.frame class.
```{r}
df <- read.table("C:/Users/etien/Documents/GitHub/mpg-envinsys-plygrnd/data_analysis/input/hessen_holzeinschlag_1997-2014.csv", sep = ";",header = TRUE,skip = 4,dec = ",")

str(df)
```
2: Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees (i.e. a similar kind of information as provided by the summary function).
```{r}
v <- df[,c(2:7)]

boxplot(v,main="Wald- und Forstwirtschaft in Hessen", xlab="Baumart", ylab="Holzeinschlag")

```

3: Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related to each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid (i.e. arrange the figures in a 2 columns and 2 rows layout).

```{r}
par(mfrow = c(2,2))

barplot(t(as.matrix(df[c(3,2)])), width = 8,beside = TRUE, space = c(0,0.5) ,names.arg = df[,1],legend.text = TRUE,
        ylab = "Holzeinschlag",
        xlab = "Jahr")



barplot(t(as.matrix(df[c(3,4)])), width = 8,beside = TRUE, space = c(0,0.5) ,names.arg = df[,1],legend.text = TRUE,
        ylab = "Holzeinschlag",
        xlab = "Jahr")

barplot(t(as.matrix(df[c(3,5)])), width = 8,beside = TRUE, space = c(0,0.5) ,names.arg = df[,1],legend.text = TRUE,
        ylab = "Holzeinschlag",
        xlab = "Jahr")


barplot(t(as.matrix(df[c(3,6)])), width = 8,beside = TRUE, space = c(0,0.5) ,names.arg = df[,1],legend.text = TRUE,
        ylab = "Holzeinschlag",
        xlab = "Jahr")
```

4: Include your opinion on what could be the key message of these figures in two sentence max.
```{r}
#Die Abbildungen geben zu erkennen, dass die Fichte, noch vor der Buche, in der Wald- und Forstwirtschaft in Hessen die wichtigste Baumart darstellt. Außerdem wird die größere Anfälligkeit der Fichte gegenüber Extremereignissen sichtbar. 
```

