---
title: "Assignment 03"
author: "Jonas Viehweger"
date: "5 11 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd("C:/Users/Jonas/Google Drive/Studium/Marburg/WS19/data_analysis")
knitr::opts_knit$set(root.dir = "C:/Users/Jonas/Google Drive/Studium/Marburg/WS19/data_analysis")
```

## 1

Read the data provided in the Excel file and “isolate” the tabulated information into a data.frame class.

```{r}
df = read.table("data/assignment_03/hessen_holzeinschlag_1997-2014.csv", sep = ";", header = T, skip = 4, nrows = 18)
class(df)
```

## 2

Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees (i.e. a similar kind of information as provided by the summary function).

```{r}
boxplot(df[,2:7], xlab = "Baumart", ylab = "Holzeinschlag", main = "Boxplots pro Baumart")
```

## 3

Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related to each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid (i.e. arrange the figures in a 2 columns and 2 rows layout).

```{r}
par(mfrow = c(2,2))

plot(df$Buche, df$Eiche)
abline(lm(df$Eiche~df$Buche), col="red")
plot(df$Buche, df$Kiefer)
abline(lm(df$Kiefer~df$Buche), col="red")
plot(df$Buche, df$Fichte)
abline(lm(df$Fichte~df$Buche), col="red")
plot(df$Buche, df$Buntholz)
abline(lm(df$Buntholz~df$Buche), col="red")
```

## 4

Include your opinion on what could be the key message of these figures in two sentence max.

```{r}
par(mfrow = c(2,2))

barplot(t(as.matrix(df[,c(3,2)])), 
        beside = TRUE,
        names.arg = df$FWJ,
        legend.text = TRUE,
        ylab = "number of individuals",
        xlab = "Length class (cm)")

barplot(t(as.matrix(df[,c(3,4)])), 
        beside = TRUE,
        names.arg = df$FWJ,
        legend.text = TRUE,
        ylab = "number of individuals",
        xlab = "Length class (cm)")

barplot(t(as.matrix(df[,c(3,5)])), 
        beside = TRUE,
        names.arg = df$FWJ,
        legend.text = TRUE,
        ylab = "number of individuals",
        xlab = "Length class (cm)")

barplot(t(as.matrix(df[,c(3,6)])), 
        beside = TRUE,
        names.arg = df$FWJ,
        legend.text = TRUE,
        ylab = "number of individuals",
        xlab = "Length class (cm)")
```
