创创
---
title: "Hausaufgabe3"
author: "Carl Ziereisen"
date: "10 November 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Step1:
Read the data provided in the Excel file and ?isolate? the tabulated information into a data.frame class.

```{r}

#Zuerst die untere Textzeile in der Exeltabelle manuell entfernen
df <- read.table("F:/Uni Marburg/1.Semester/Fernerkundung/mpg-envinsys-plygrnd/mpg-envinfosys-teams-2019-eddi-und-carl/src/hessen_holzeinschlag_1997-2014.csv", header = TRUE, sep = ";", skip = 4)

str(df)

```

Step2:
Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees (i.e. a similar kind of information as provided by the summary function).

```{r}
v <- df[,c(2:7)]



boxplot(v, main = "Boxplots von allen Baumarten", xlab="Baumart", ylab="Anzahl Holzeinschlag von 1997-2014")



```

Step3:
Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related to each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid (i.e. arrange the figures in a 2 columns and 2 rows layout).

```{r}


par(mar=c(5,4,2,6))
#Erweiterung des Plotrahmen

par(mfrow = c(2,2))
#Zum Ploten mehrerer Plots innerhalb eines Rahmens in einer 2x2 Anordnung

barplot(t(as.matrix(df[c(3,2)])), width = 8,beside = TRUE, space = c(0,1) ,names.arg = df[,1],las=2,cex.names=0.75,col=c("black","darkgrey"),
        ylab = "Anzahl Holzeinschlag",
        xlab = "Jahr")
legend(x='topleft',legend=c("Buche","Eiche"),cex=1,col=c("black","darkgrey"),title="Baumart",inset=c(1,0), xpd=TRUE, bty="n",pch=15)

# "t"" vor "(as.matrix)" fr Umsortierung der Achsen, 
#"inset=c(1,0), xpd=TRUE, bty="n",pch=15 + Z40" zum ploten der Legende auerhalb der Grafik  
#las=2 Zur Ausrichtung des y-Achsenlabels

barplot(t(as.matrix(df[c(3,4)])), width = 8,beside = TRUE, space = c(0,1) ,names.arg = df[,1],las=2,cex.names=0.75,col=c("black","darkgrey"),
        ylab = "Anzahl Holzeinschlag",
        xlab = "Jahr")
legend(x='topleft',legend=c("Buche","Buntholz"),cex=1,col=c("black","darkgrey"),title="Baumart",inset=c(1,0), xpd=TRUE, bty="n",pch=15)

barplot(t(as.matrix(df[c(3,5)])), width = 8,beside = TRUE, space = c(0,1) ,names.arg = df[,1],las=2,cex.names=0.75,col=c("black","darkgrey"),
        ylab = "Anzahl Holzeinschlag",
        xlab = "Jahr")
legend(x='topleft',legend=c("Buche","Fichte"),cex=1,col=c("black","darkgrey"),title="Baumart",inset=c(1,0), xpd=TRUE, bty="n",pch=15)

barplot(t(as.matrix(df[c(3,6)])), width = 8,beside = TRUE, space = c(0,1) ,names.arg = df[,1],las=2,cex.names=0.75,col=c("black","darkgrey"),
        ylab = "Anzahl Holzeinschlag",
        xlab = "Jahr")
legend(x='topleft',legend=c("Buche","Kiefer"),cex=1,col=c("black","darkgrey"),title="Baumart",inset=c(1,0), xpd=TRUE, bty="n",pch=15)


```


Step4:
Include your opinion on what could be the key message of these figures in two sentence max.

Betrachtet man die vier Plots in ihrer Gesamtheit faellt auf, dass besonders die Fichte im Jahr 2007 eine exrem hohen Holzeinschlag verzeichnet. Dies ist auf das starke Sturmtief Kyrill vom Januar 2007 zurueckzufueren.   
创创
